---
title: "Individual2"
author: "Danny Nguyen"
date: "February 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
data(happy, package="productplots")
head(happy)
summary(happy, package="productplots")
na.omit(happy$happy)
typeof(happy$age)
as.numeric(happy$age)
head(happy)



#explore 2 variables
library(ggplot2)
ggplot(data = happy, aes(x = happy, fill = age, color=as.factor(age))) + geom_bar()
ggplot(data = happy, aes(x = happy, fill = sex, color=as.factor(sex))) + geom_bar()
ggplot(data = happy, aes(x = happy, fill = year, color=as.factor(year))) + geom_bar()


#explore 4 variables
ggplot(data = happy, aes(x = happy, fill = age, color=as.factor(age))) +
  geom_bar() + 
  facet_grid(. ~ degree)

ggplot(data = happy, aes(x = happy, fill = sex, color=as.factor(sex))) +
  geom_bar() + 
  facet_grid(. ~ degree)

ggplot(data = happy, aes(x = happy, fill = year, color=as.factor(year))) +
  geom_bar() + 
  facet_grid(. ~ degree)
```

# From the data set, I can only interpret that the happiness levels vary if based on level of education. while there is a relatively larger number of data entries for high school, there appears to be a somewhat similar pattern of distribution among the different degree levels. While I believe I managed to convert the missing values to NA, tt does seem to show a small chunk of the data of people that didn't answer their happiness levels.